Gammapy: A Python package for gamma-ray astronomy

### 2022-12-07 src/ms-review.tex
Correct typo
modify abstract

\abstract{
	% TODO: the feature are still to detailed and partly copy and pasted form the ICRS abstract...avoid this
	% context heading (optional)
	% {} leave it empty if necessary
	%{Gammapy context:}
	Historically, the data and the analysis software of \gammaray astronomy experiments are
	proprietary to the collaborations operating them. The next generation of \gammaray instruments, as the Cherenkov Telescope Array
	(CTA) will be operated as open observatories, with public
	data. This introduces the need to have a high-level analysis software available to the astronomical community. In
	this article we present the first major release of \gammapy, the Long-term Support (LTS) v1.0, a
	community-developed open-source Python package for \gammaray astronomy. We
	present its general design and provide an
	overview of the analysis methods and features it implements. Starting from
	event lists and a description of the specific instrument response functions
	(IRF) stored in open FITS based data formats, \gammapy implements the reduction
	of the input data and instrument response to binned WCS, HEALPix or region based
	data structures. Thereby it
	handles the dependency of the IRFs with time, energy as well as position on the
	sky. It offers a variety of background estimation methods for spectral, spatial
	and spectro-morphological analysis. Counts, background and IRFs data are
	bundled in datasets and can be serialised, rebinned and stacked. \gammapy
	supports to model binned data using Poisson
	maximum likelihood fitting. It comes with built-in spectral, spatial and
	temporal models, support for particle radiation emission spectra as well as
	support for custom user models, to model e.g.,
	energy dependent morphology of \gammaray sources. Multiple datasets can be
	combined in a joint-likelihood approach to either handle time dependent IRFs,
	different classes of events or combination of data from multiple instruments.
	Gammapy also implements methods to estimate flux points, likelihood
	profiles per energy bin, light curves as well as flux and signficance maps in
	energy bins.  We further describe the general
	development approach and how \gammapy integrates into ecosystem of other
	scientific and astronomical Python packages. We also present analysis examples
	with simulated CTA data and provide results of scientific validation analyses
	using data of existing instruments such as \hess and \fermi.

	% The \gammaray can be considered as the last frontier
	% In the last two decades the measurement of \gammaray emission from the universe has
	% evolved from a niche

	% aims heading (mandatory)
	%{Gammapy aims}
	%Reproducible analyses, share algorithms etc.

	% methods heading (mandatory)
	%{Gammapy methods}

	% results heading (mandatory)
	%{Gammapy results}

	% conclusions heading (optional), leave it empty if necessary
	%{Gammapy conclusions}
}

@@

\subsection{Events and Instrument Response Functions: the Data Level 3}

\gammaray data at the Data Level 3 (DL3) consists in lists of gamma-like events and their
corresponding instrument response functions (IRFs). The latter include the effective area,
point spread function (PSF), energy dispersion and residual hadronic background.

In the most general way we can write the expected number of detected events from a given astrophysical source
of \gammaray at measured position $p$ and energy $E$:
\begin{align}
   N(p, E) {\rm d}p {\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true})\\
   &\times \Phi(p_{\rm true}, E_{\rm true}) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
\end{align}
where
\begin{itemize}
\item $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response
\item $\Phi(p_{\rm true}, E_{\rm true})$ is the parametrised sky flux model
\item $t_{\rm obs}$ is the observation time
\end{itemize}

@@

An additional component of DL3 IRFs is the residual hadronic background model $$.
It represents the  intensity of mis-identified charged particles events that are expected
during an observation. It is defined as a function of the measured position in the field-of-view
and measured energy.

In total, the expected number of events in a \gammaray observation is given by:
\begin{align}
N(p, E) {\rm d}p {\rm d}E =  E_{\rm disp} \star (PSF \star A_{\rm eff} t_{\rm obs} t_{\rm obs}) + Bkg(p, E)
\end{align}

\subsection{Data analysis workflow}

In Gammapy, the handling of DL3 data is performed by classes and methods
in the \code{gammapy.data} (see Section~\ref{ssec:gammapy-data}) and the \code{gammapy.irf}
(see Section~\ref{ssec:gammapy-irf}) subpackages.

@@

The next step of the analysis is the data reduction, where all observation events and instrument
responses are filled into or projected onto a common physical coordinate system, defined by
a map geometry. The definition of the map geometry typically consists of a spectral dimension
defined by a binned energy axis and of spatial dimensions, which either define 
a spherical projection from celestial coordinates to a pixelised image space
(for 3-dimensional or cube analysis) or a region on the sky (for regular spectral analysis).
The \code{gammapy.maps} subpackage provides general multidimensional geometry objects
(\code{Geom}) and the associated data structures (\code{Maps}) (see Section~\ref{ssec:gammapy-maps}).

>>>>

\abstract{

	{Context} In the last two decades the measurement of \gammaray emission from the universe has
	evolved from a niche area of closed collaborations operating with proprietary data and software into
	an active and exciting field of astrophysics. The next generation of \gammaray instruments,
	such as the Cherenkov Telescope Array (CTA), will be operated as open observatories with publicly available
	data, which will require open high-level astronomy software customised for high energy astrophysics.

	{Aims} In this article, we present the first the Long-term Support (LTS) release of \gammapy v1.0. \gammapy
	is a community-developed, open-source Python package for \gammaray astronomy. Integrated into the general
	python eco-system, it is built on Numpy, Scipy and Astropy and uses open FITS based data formats for serialisation.
	It provides a uniform platform for reduction and modelling of data from many \gammaray instruments.

	{Methods} Starting from event list and instrument response functions at the so called "Data Level 3",
	\gammapy provides pipelines for reduction of the input data to binned WCS, HEALPix or region based data structures.
	A variety of background reduction methods, including traditional techniques like the Reflected and Ring regions,
	as well as novel 3D Field of View Likelihood techniques, are supported. The binned data can then be modelled
	using Poisson maximum likelihood fitting. While a variety of in-built spectral, temporal and spatial models
	are supplied, it also supports implementation of custom user defined models. Estimation of flux points, likelihood
	profiles and light curves are also implemented.

	{Results} The flexible API allows a joint likelihood analysis between different datasets,
	thus providing a simple platform for handling time dependent instrument responses,
	different events classes, or combining data from multiple separate instruments. The results are continuously
	validated with previously published ones. We show analysis examples using open data from various observatories: \fermi., \hess , MAGIC, CTA (simulated),
	and HAWC. 
}

@@

In the most general way we can write the expected number of detected events at measured
position $p$ and energy $E$:
\begin{align}
   N(p, E) {\rm d}p {\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true})\\
   &\times \Phi(p_{\rm true}, E_{\rm true}) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
\end{align}
where
\begin{itemize}
\item $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response
\item $\Phi(p_{\rm true}, E_{\rm true})$ is the parametrised sky flux model
\item $t_{\rm obs}$ is the observation time
\end{itemize}

@@

\gammaray data at the Data Level 3 (DL3) therefore consists in lists of gamma-like events and their
corresponding instrument response functions (IRFs). The latter include the aforementioned
effective area, point spread function (PSF), energy dispersion and residual hadronic background.
The handling of DL3 data is performed by classes and methods
in the \code{gammapy.data} (see Section~\ref{ssec:gammapy-data}) and the \code{gammapy.irf}
(see Section~\ref{ssec:gammapy-irf}) subpackages.

@@

The next step of the analysis is the data reduction, where all observation events and instrument
responses are filled into or projected onto a common physical coordinate system, defined by
a map geometry. The definition of the map geometry typically consists of a spectral dimension
defined by a binned energy axis and of a spatial dimension, which either defines 
a spherical projection from celestial coordinates to an pixelised image space
(for 3-dimensional or cube analysis) or a region on the sky (for regular spectral analysis).
The \code{gammapy.maps} subpackage provides general multidimensional geometry objects
(\code{Geom}) and the associated data structures (\code{Maps}) (see Section~\ref{ssec:gammapy-maps}).
